---
title: "Foodmapping Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Foodmapping}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = TRUE, include = FALSE}
library(pander)
library(Foodmapping)
```


## Compute fuzzy matching similarity scores using Partial Token Sort Ratio 

The v_fz_tk_sort_r compute similarities between two strings (e.g.two food item
names), using the Partial_token_sort_ratio method. This method returns the ratio
of the most similar substring as a number between 0 and 100 but sorting the
token before comparing. Applied to the comparison of food names, a ratio close
to 100 indicates that one food name is fully found in the second food name.


```{r , echo = TRUE}
v_fz_tk_sort_r( "Tomatoes" , "raw. tomatoes" )
```

High ratio reflect high similarity between food names:
```{r , echo = TRUE}
v_fz_tk_sort_r( "Tomatoe and basil soup" , "Tomatoe soup with basil" )
```

Conversely, smaller ratios indicate no / little similarities between food names

```{r , echo = TRUE}
v_fz_tk_sort_r( "Tomatoes" , "Carot soup" )
```



## Compute fuzzy similarities from a large list of food names

The v_fz_tk_sort_r function can be applied for element-wise comparisons between
two vectors.

```{r , echo = TRUE}
data(food_sample)

food_names1 <- food_sample$FOODNAME_ENG
food_names2 <- food_sample$FOODNAME_ENG_COMP

scores <- v_fz_tk_sort_r( food_names1 , food_names2)

results <- data.frame(
  name1 = food_names1,
  name2 = food_names2,
  score = scores
)
pander(head(results), split.table = Inf )
```


The v_fz_tk_sort_r is optimized for a large number of comparison and compute the
similarity metrics in parallel.

```{r , echo = TRUE}
# make a large example of  10'000 comparisons - takes < 5 seconds
large_example <- expand.grid( A = food_names1[ 1:100 ] , B  = food_names2[ 1:100 ] ) # create all pairwise comparisons
dim( large_example )
system.time(
  scores <- v_fz_tk_sort_r( as.character( large_example$A ), as.character( large_example$B ) )
)
```




